### 2016-02-12 prepReport/intro.tex
Corrected References
FINAL Version

In Chapter~\ref{chap:workPlan}, the work plan for the Dissertation work is detailed as \emph{tasks} in Section~\ref{sec:wp_tasks_td}, and their temporal arrangement is pictured in a Gantt chart in Section~\ref{sec:wp_tasks_gantt}. Furthermore, the description of the Hardware and Software resources that I will be utilizing during the course of my work is done in Section~\ref{sec:wp_sh}

Finally, in Chapter~\ref{chap:earlyWork} I will present some of the work that I have already concluded.

>>>>

In Chapter~\ref{chap:earlyWork} I will present some of the work that I have already concluded.

Finally, in Chapter~\ref{chap:workPlan}, the work plan for the Dissertation work is detailed as \emph{tasks} in Section~\ref{sec:wp_tasks_td}, and their temporal arrangement is pictured in a Gantt chart in Section~\ref{sec:wp_tasks_gantt}. Furthermore, the description of the Hardware and Software resources that I will be utilizing during the course of my work is done in Section~\ref{sec:wp_sh}
